---
title: "dsClusterAnalysisClient"
author: 
- name: Florian Schwarz
  affiliation: 
  - &isglobal German Institute of Human Nutrition Potsdam-Rehbruecke
  email: Florian.Schwarz@dife.de
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{dsClusterAnalysisClient}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  comment = "",
  warning = FALSE,
  message = FALSE,
  cache = TRUE
)
```

## Introduction

In order to use this vignette, you need a Virtual Machine running imitating the server side of a real-world Opal connection. In order to do this, follow the instructions displayed here: https://data2knowledge.atlassian.net/wiki/spaces/DSDEV/pages/1657602074/Virtual+Machines+Guides.

Note: This section needs to be expanded with detailed information!!!

192.168.56.150:8080 instead of the 192.168.56.100:8080 further information required


## Installation of devtools and dsClusterAnalysisClient

```{r install_dsClusterAnalysis, eval = FALSE}
install.packages("devtools")
library(devtools)
devtools::install_github("FlorianSchw/dsClusterAnalysisClient")


```

## Loading of all relevant Libraries


```{r cache = FALSE}
library(dsBaseClient)
library(dsClusterAnalysisClient)
library(DSOpal)
```

## Bulding a connection to the Virtual Machine

```{r child='functions/initialize_connection.Rmd', include=TRUE}
```


## Creating the cluster Plot from the dataset


```{r child='functions/clusterPlot.Rmd', include=TRUE}
```












